NumPy---Array Programming in Python

### 2020-02-16 authors.tex
Update PGM affil

\author[1]{Charles R. Harris}
\author[2,3,4,*]{K. Jarrod Millman}
\author[5,2,4,*]{St\'efan J. van der Walt}
\author[6,*]{Ralf Gommers}
\author[7]{Pauli Virtanen}
\author[8]{David Cournapeau}
\author[9]{Eric Wieser}
\author[10]{Julian Taylor}
\author[4]{Sebastian Berg}
\author[11]{Nathaniel J. Smith}
\author[12]{Robert Kern}
\author[4]{Matti Picus}
\author[13]{Stephan Hoyer}
\author[14]{Marten H. van Kerkwijk}
\author[2,15]{Matthew Brett}
\author[16]{Allan Haldane}
\author[17]{Jaime Fern\'andez del R\'io}
\author[18,19]{Mark Wiebe}
\author[6,20,21]{Pearu Peterson}
\author[22]{Pierre G\'erard-Marchant}
\author[23]{Kevin Sheppard}
\author[24]{Tyler Reddy}
\author[4]{Warren Weckesser}
\author[6]{Hameer Abbasi}
\author[25]{Christoph Gohlke}
\author[6]{Travis E. Oliphant}
\affil[1]{Independent Researcher, Logan, Utah, USA}
\affil[2]{Helen Wills Neuroscience Institute, University of California, Berkeley, Berkeley, CA, USA}
\affil[3]{Division of Biostatistics, University of California, Berkeley, Berkeley, CA, USA}
\affil[4]{Berkeley Institute for Data Science, University of California, Berkeley, Berkeley, CA, USA}
\affil[5]{Applied Mathematics, Stellenbosch University, Stellenbosch, South Africa}
\affil[6]{Quansight LLC, Austin, TX, USA}
\affil[7]{Department of Physics and Nanoscience Center, University of Jyv\"askyl\"a, Jyv\"askyl\"a, Finland}
\affil[8]{Mercari JP, Tokyo, Japan}
\affil[9]{Department of Engineering, University of Cambridge, Cambridge, UK}
\affil[10]{Independent Researcher, Karlsruhe, Germany}
\affil[11]{Independent Researcher, Berkeley, CA, USA}
\affil[12]{Enthought, Inc., Austin, TX, USA}
\affil[13]{Google Research, Mountain View, CA, USA}
\affil[14]{Department of Astronomy \& Astrophysics, University of Toronto, Toronto, ON, Canada}
\affil[15]{School of Psychology, University of Birmingham, Edgbaston, Birmigham, UK}
\affil[16]{Department of Physics, Temple University, Philadelphia, PA, USA}
\affil[17]{Google, Zurich, Switzerland}
\affil[18]{Department of Physics and Astronomy, The University of British Columbia, Vancouver, BC, Canada}
\affil[19]{Amazon, Seattle, Washington, USA}
\affil[20]{Independent Researcher, Saue, Estonia}
\affil[21]{Department of Mechanics and Applied Mathematics, Institute of Cybernetics at Tallinn Technical University, Tallinn, Estonia}
\affil[22]{France-IX Services, Paris, France}
\affil[23]{Department of Economics, University of Oxford, Oxford, UK}
\affil[24]{CCS-7, Los Alamos National Laboratory, Los Alamos, NM, USA}
\affil[25]{Laboratory for Fluorescence Dynamics, Biomedical Engineering Department, University of California, Irvine, Irvine, CA, USA}
\affil[*]{numpy.articles@gmail.com}

>>>>

\author[1]{Charles R. Harris}
\author[2,3,4,*]{K. Jarrod Millman}
\author[5,2,4,*]{St\'efan J. van der Walt}
\author[6,*]{Ralf Gommers}
\author[7]{Pauli Virtanen}
\author[8]{David Cournapeau}
\author[9]{Eric Wieser}
\author[10]{Julian Taylor}
\author[4]{Sebastian Berg}
\author[11]{Nathaniel J. Smith}
\author[12]{Robert Kern}
\author[4]{Matti Picus}
\author[13]{Stephan Hoyer}
\author[14]{Marten H. van Kerkwijk}
\author[2,15]{Matthew Brett}
\author[16]{Allan Haldane}
\author[17]{Jaime Fern\'andez del R\'io}
\author[18,19]{Mark Wiebe}
\author[6,20,21]{Pearu Peterson}
\author[22,23]{Pierre G\'erard-Marchant}
\author[24]{Kevin Sheppard}
\author[25]{Tyler Reddy}
\author[4]{Warren Weckesser}
\author[6]{Hameer Abbasi}
\author[26]{Christoph Gohlke}
\author[6]{Travis E. Oliphant}
\affil[1]{Independent Researcher, Logan, Utah, USA}
\affil[2]{Helen Wills Neuroscience Institute, University of California, Berkeley, Berkeley, CA, USA}
\affil[3]{Division of Biostatistics, University of California, Berkeley, Berkeley, CA, USA}
\affil[4]{Berkeley Institute for Data Science, University of California, Berkeley, Berkeley, CA, USA}
\affil[5]{Applied Mathematics, Stellenbosch University, Stellenbosch, South Africa}
\affil[6]{Quansight LLC, Austin, TX, USA}
\affil[7]{Department of Physics and Nanoscience Center, University of Jyv\"askyl\"a, Jyv\"askyl\"a, Finland}
\affil[8]{Mercari JP, Tokyo, Japan}
\affil[9]{Department of Engineering, University of Cambridge, Cambridge, UK}
\affil[10]{Independent Researcher, Karlsruhe, Germany}
\affil[11]{Independent Researcher, Berkeley, CA, USA}
\affil[12]{Enthought, Inc., Austin, TX, USA}
\affil[13]{Google Research, Mountain View, CA, USA}
\affil[14]{Department of Astronomy \& Astrophysics, University of Toronto, Toronto, ON, Canada}
\affil[15]{School of Psychology, University of Birmingham, Edgbaston, Birmigham, UK}
\affil[16]{Department of Physics, Temple University, Philadelphia, PA, USA}
\affil[17]{Google, Zurich, Switzerland}
\affil[18]{Department of Physics and Astronomy, The University of British Columbia, Vancouver, BC, Canada}
\affil[19]{Amazon, Seattle, Washington, USA}
\affil[20]{Independent Researcher, Saue, Estonia}
\affil[21]{Department of Mechanics and Applied Mathematics, Institute of Cybernetics at Tallinn Technical University, Tallinn, Estonia}
\affil[22]{Department of Biological and Agricultural Engineering, University of Georgia, Athens, GA}
\affil[23]{France-IX Services, Paris, France}
\affil[24]{Department of Economics, University of Oxford, Oxford, UK}
\affil[25]{CCS-7, Los Alamos National Laboratory, Los Alamos, NM, USA}
\affil[26]{Laboratory for Fluorescence Dynamics, Biomedical Engineering Department, University of California, Irvine, Irvine, CA, USA}
\affil[*]{numpy.articles@gmail.com}
